Notes: New gaugings in 3d from three-form

### 2023-06-20 Draft_3dH3.tex
Change in hyperref.
Solving issues with hyperref and arXiv.

\documentclass[a4paper, 11pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsfonts,slashed}
%\usepackage{arydshln}
%\usepackage[greek,english]{babel}
%\usepackage{cancel}
%\usepackage{upgreek}
\usepackage{float}
\usepackage{cite}
%\usepackage{url}
\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{epsfig}
%\usepackage{isomath}
\usepackage{latexsym,amssymb}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}
%\usepackage{fontenc}
\usepackage{graphicx,tikz}
\usetikzlibrary{arrows.meta,arrows}
\usepackage{multirow}
\setcounter{MaxMatrixCols}{13}
%\usepackage{xfrac}
%\usepackage[T1]{fontenc}
\usepackage{textcomp}
%\usepackage{lmodern}
\usepackage{xcolor}
\usepackage{mathtools}
\usepackage{stmaryrd}
%%%%%%%%% Packages to show breakings %%%%%%%%%
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}

@@

%  PDF specials
%\newif\ifpdf
\usepackage{ifpdf}
\ifx\pdfoutput\undefined
\pdffalse
\usepackage{cite}
\else
\pdfoutput=1
\pdftrue
%\usepackage[pdftex]{hyperref}
\pdfcompresslevel=9
\fi
\DeclareFontFamily{OMS}{rsfs}{\skewchar\font'60}
\DeclareFontShape{OMS}{rsfs}{m}{n}{<-5>rsfs5 <5-7>rsfs7 <7->rsfs10 }{}
\DeclareSymbolFont{rsfs}{OMS}{rsfs}{m}{n}
\DeclareSymbolFontAlphabet{\Scr}{rsfs}
\newcommand{\RRB}[2]{\makebox[#1]{$\left.\rule{0pt}{#2}\right)$}}
\newcommand{\LRB}[2]{\makebox[#1]{$\left(\rule{0pt}{#2}\right.$}}
\newcommand{\RSB}[2]{\makebox[#1]{$\left.\rule{0pt}{#2}\right]$}}
\newcommand{\LSB}[2]{\makebox[#1]{$\left[\rule{0pt}{#2}\right.$}}
\newcommand{\gr}[1]{\begin{greek}#1\end{greek}}
\setlength{\parskip}{0pt} \setlength{\parindent}{0.5cm}
\setcounter{footnote}{0}
\renewcommand{\theequation}{\thesection.\arabic{equation}}
\numberwithin{equation}{section}
\def\be{\begin{equation}}
	\def\ee{\end{equation}}
\def\ba{\begin{array}}
	\def\ea{\end{array}}
\newcommand{\ho}[1]{$\, ^{#1}$}
\newcommand{\hoch}[1]{$\, ^{#1}$}
\newcommand{\bea}{\begin{eqnarray}}
	\newcommand{\eea}{\end{eqnarray}}
\newcommand{\ds}{\displaystyle}
\newcommand{\BNA}{\makebox[0.8em]{\tiny$b\neq a$}}
\newcommand{\notEq}[2]{\makebox[0.8em]{\tiny$#1\neq #2$}}
\newcommand{\ph}{\alpha}
\newcommand{\scal}{z}
\newcommand{\bscal}{\bar\scal}
\newcommand{\scalC}{\pi}
%%%%%%%%%%%%%%%%% formatting
\textwidth 165mm \textheight 220mm \topmargin 0pt \oddsidemargin 2mm
%%% macros
\newcommand{\rmg}[1]{\mbox{{\small \textgreek{#1}}}}
\newcommand{\rmgg}[1]{\mathrm{#1}}
\newcommand{\ft}[2]{{\textstyle\frac{#1}{#2}}}
\newcommand{\ts}[1]{\widetilde{#1}}

@@

\section{Representations of \texorpdfstring{$D^{1}(2,1;\alpha)$}{D(2,1,a)}} \label{app:d21a}
The supergroup $D^{1}(2,1;\alpha)$ has
\begin{equation}
	{\rm SU}(1,1)\times{\rm SU}(2)\times\ts{{\rm SU}(2)}
\end{equation}
as its even part. Its multiplets are labelled by the spins $\ell$ and $\ts{\ell}$ of each ${\rm SU}(2)$ factor and the eigenvalue $h$ of the $\mathfrak{su}(1,1)\simeq\mathfrak{sl}(2,\mathbb{R})$ generator. Generic short multiplets $[\ell,\ts{\ell}]_{\rm s}$ are given by~\cite{deBoer:1999gea,Eberhardt:2017fsi}
\begin{equation}
	\begin{array}{cc}
	 h_{0} & \big(\ell,\ts{\ell}\big) \\[5pt]
	 h_{0} + \nicefrac{1}{2} & \big(\ell+\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big) \oplus \big(\ell-\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big) \oplus \big(\ell-\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}\big) \\[5pt]
	 h_{0}+1 & \big(\ell,\ts{\ell}-1\big) \oplus \big(\ell,\ts{\ell}\big) \oplus \big(\ell-1,\ts{\ell}\big) \\[5pt]
	 h_{0} + \nicefrac{3}{2} & \big(\ell-\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big)\,,
	\end{array}
\end{equation}
with $h_{0}=(\alpha\,\ell+\ts{\ell})/(1+\alpha)$. Shortenings occur for $\ell<1$ or $\ts{\ell}<1$~\cite{deBoer:1999gea}. For instance:
\begin{equation}
	[0,0]_{\rm s}:\quad h_{0}=0 \quad (0,0),\qquad  [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}: \begin{array}{cc}
	 h_{0}=\nicefrac{1}{2} & \big(\nicefrac{1}{2},\nicefrac{1}{2}\big) \\[5pt]
	 1 & \big(1,0\big) \oplus \big(0,0\big) \oplus \big(0,1\big) \\[5pt]
	 \nicefrac{3}{2} & \big(\nicefrac{1}{2},\nicefrac{1}{2}\big) \\[5pt]
	 2 & \big(0,0\big)\,.
	\end{array}
\end{equation}

Two short multiplets can combine into a long multiplets $[\ell,\ts{\ell}]$ as follows:
\begin{equation}
 	[\ell,\ts{\ell}] = [\ell,\ts{\ell}]_{\rm s} \oplus [\ell+\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}]_{\rm s}\,.
\end{equation}
The value of $h$ is then not constrained. The explicit content of the long representation $[\ell,\ts{\ell}]$  is
\begin{equation}
	\begin{array}{cc}
	 h & \big(\ell,\ts{\ell}\big) \\[5pt]
	 h + \nicefrac{1}{2} & \big(\ell+\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}\big) \oplus\big(\ell+\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big) \oplus \big(\ell-\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}\big) \oplus \big(\ell-\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big) \\[5pt]
	 h+1 & \big(\ell+1,\ts{\ell}\big) \oplus \big(\ell,\ts{\ell}-1\big) \oplus \big(\ell,\ts{\ell}\big) \oplus \big(\ell,\ts{\ell}\big) \oplus \big(\ell-1,\ts{\ell}\big)\oplus \big(\ell,\ts{\ell}+1\big) \\[5pt]
	 h + \nicefrac{3}{2} & \big(\ell+\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}\big) \oplus\big(\ell+\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big) \oplus \big(\ell-\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}\big) \oplus \big(\ell-\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big) \\[5pt]
	 h + 2 & \big(\ell,\ts{\ell}\big)\,.
	\end{array}
\end{equation}

>>>>

\documentclass[a4paper, 11pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsfonts,slashed}
%\usepackage{arydshln}
%\usepackage[greek,english]{babel}
%\usepackage{cancel}
%\usepackage{upgreek}
\usepackage{float}
\usepackage{cite}
%\usepackage{url}
\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{epsfig}
%\usepackage{isomath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{xcolor}
\usepackage{hyperref}
\definecolor{darkorange}{RGB}{166, 88, 0}
\hypersetup{colorlinks=true,
        pdfstartview=FitV,
        linkcolor= darkorange,% mydarkorange,
        citecolor= darkorange, %mydarkorange,
        urlcolor= gray!60!black,
        hypertexnames=false,
        linktoc=page}
%\usepackage{fontenc}
\usepackage{graphicx,tikz}
\usetikzlibrary{arrows.meta,arrows}
\usepackage{multirow}
\setcounter{MaxMatrixCols}{13}
%\usepackage{xfrac}
%\usepackage[T1]{fontenc}
\usepackage{textcomp}
%\usepackage{lmodern}
\usepackage{mathtools}
\usepackage{stmaryrd}
%%%%%%%%% Packages to show breakings %%%%%%%%%
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}

@@

% %  PDF specials
% %\newif\ifpdf
% \usepackage{ifpdf}
% \ifx\pdfoutput\undefined
% \pdffalse
% \usepackage{cite}
% \else
% \pdfoutput=1
% \pdftrue
% %\usepackage[pdftex]{hyperref}
% \pdfcompresslevel=9
% \fi
\DeclareFontFamily{OMS}{rsfs}{\skewchar\font'60}
\DeclareFontShape{OMS}{rsfs}{m}{n}{<-5>rsfs5 <5-7>rsfs7 <7->rsfs10 }{}
\DeclareSymbolFont{rsfs}{OMS}{rsfs}{m}{n}
\DeclareSymbolFontAlphabet{\Scr}{rsfs}
\newcommand{\RRB}[2]{\makebox[#1]{$\left.\rule{0pt}{#2}\right)$}}
\newcommand{\LRB}[2]{\makebox[#1]{$\left(\rule{0pt}{#2}\right.$}}
\newcommand{\RSB}[2]{\makebox[#1]{$\left.\rule{0pt}{#2}\right]$}}
\newcommand{\LSB}[2]{\makebox[#1]{$\left[\rule{0pt}{#2}\right.$}}
\newcommand{\gr}[1]{\begin{greek}#1\end{greek}}
\setlength{\parskip}{0pt} \setlength{\parindent}{0.5cm}
\setcounter{footnote}{0}
\renewcommand{\theequation}{\thesection.\arabic{equation}}
\numberwithin{equation}{section}
\def\be{\begin{equation}}
	\def\ee{\end{equation}}
\def\ba{\begin{array}}
	\def\ea{\end{array}}
\newcommand{\ho}[1]{$\, ^{#1}$}
\newcommand{\hoch}[1]{$\, ^{#1}$}
\newcommand{\bea}{\begin{eqnarray}}
	\newcommand{\eea}{\end{eqnarray}}
\newcommand{\ds}{\displaystyle}
\newcommand{\BNA}{\makebox[0.8em]{\tiny$b\neq a$}}
\newcommand{\notEq}[2]{\makebox[0.8em]{\tiny$#1\neq #2$}}
\newcommand{\ph}{\alpha}
\newcommand{\scal}{z}
\newcommand{\bscal}{\bar\scal}
\newcommand{\scalC}{\pi}
%%%%%%%%%%%%%%%%% formatting
\textwidth 165mm \textheight 220mm \topmargin 0pt \oddsidemargin 2mm
%%% macros
\newcommand{\rmg}[1]{\mbox{{\small \textgreek{#1}}}}
\newcommand{\rmgg}[1]{\mathrm{#1}}
\newcommand{\ft}[2]{{\textstyle\frac{#1}{#2}}}
\newcommand{\ts}[1]{\widetilde{#1}}

@@

\section{Representations of \texorpdfstring{$D^{1}(2,1;\alpha)$}{D(2,1,a)}} \label{app:d21a}
The supergroup $D^{1}(2,1;\alpha)$ has
\begin{equation}
	{\rm SU}(1,1)\times{\rm SU}(2)\times\ts{{\rm SU}(2)}
\end{equation}
as its even part. Its multiplets are labelled by the spins $\ell$ and $\ts{\ell}$ of each ${\rm SU}(2)$ factor and the eigenvalue $h$ of the $\mathfrak{su}(1,1)\simeq\mathfrak{sl}(2,\mathbb{R})$ generator. Generic short multiplets $[\ell,\ts{\ell}]_{\rm s}$ are given by~\cite{deBoer:1999gea,Eberhardt:2017fsi}
\begin{equation}
	\begin{array}{cc}
	 h_{0} & \big(\ell,\ts{\ell}\big) \\[5pt]
	 h_{0} + \nicefrac{1}{2} & \big(\ell+\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big) \oplus \big(\ell-\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big) \oplus \big(\ell-\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}\big) \\[5pt]
	 h_{0}+1 & \big(\ell,\ts{\ell}-1\big) \oplus \big(\ell,\ts{\ell}\big) \oplus \big(\ell-1,\ts{\ell}\big) \\[5pt]
	 h_{0} + \nicefrac{3}{2} & \big(\ell-\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big)\,,
	\end{array}
\end{equation}
with $h_{0}=(\alpha\,\ell+\ts{\ell})/(1+\alpha)$. Shortenings occur for $\ell<1$ or $\ts{\ell}<1$~\cite{deBoer:1999gea}. For instance:
\begin{equation}
	[0,0]_{\rm s}:\quad h_{0}=0 \quad (0,0),\qquad  [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}: \begin{array}{cc}
	 h_{0}=\nicefrac{1}{2} & \big(\nicefrac{1}{2},\nicefrac{1}{2}\big) \\[5pt]
	 1 & \big(1,0\big) \oplus \big(0,0\big) \oplus \big(0,1\big) \\[5pt]
	 \nicefrac{3}{2} & \big(\nicefrac{1}{2},\nicefrac{1}{2}\big) \\[5pt]
	 2 & \big(0,0\big)\,.
	\end{array}
\end{equation}
Two short multiplets can combine into a long multiplets $[\ell,\ts{\ell}]$ as follows:
\begin{equation}
 	[\ell,\ts{\ell}] = [\ell,\ts{\ell}]_{\rm s} \oplus [\ell+\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}]_{\rm s}\,.
\end{equation}
The value of $h$ is then not constrained. The explicit content of the long representation $[\ell,\ts{\ell}]$  is
\begin{equation}
	\begin{array}{cc}
	 h & \big(\ell,\ts{\ell}\big) \\[5pt]
	 h + \nicefrac{1}{2} & \big(\ell+\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}\big) \oplus\big(\ell+\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big) \oplus \big(\ell-\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}\big) \oplus \big(\ell-\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big) \\[5pt]
	 h+1 & \big(\ell+1,\ts{\ell}\big) \oplus \big(\ell,\ts{\ell}-1\big) \oplus \big(\ell,\ts{\ell}\big) \oplus \big(\ell,\ts{\ell}\big) \oplus \big(\ell-1,\ts{\ell}\big)\oplus \big(\ell,\ts{\ell}+1\big) \\[5pt]
	 h + \nicefrac{3}{2} & \big(\ell+\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}\big) \oplus\big(\ell+\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big) \oplus \big(\ell-\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}\big) \oplus \big(\ell-\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big) \\[5pt]
	 h + 2 & \big(\ell,\ts{\ell}\big)\,.
	\end{array}
\end{equation}
